Turoman-2022

### 2024-10-22 doc/charting/Dora-2024.qmd
update data extraction from my studies

## Tools

### Specific tools mentioned - their function - where in the researh process used

::: content-hidden
For instance: "OSF - pre-registration - planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

-

@@

::: content-hidden
For instance: "Develop forms of legitimate peripheral participation."

These are bit of information and recommendations for governance of the
project.
:::

@@

### Workflow

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

-

@@

::: content-hidden
For instance: "few resources for open collaboration, none were open and
they were valued poorly compared to other practices"

What does the paper write is the need for education in the field?
:::

@@

::: content-hidden
For instance: "lack of education"

Which barriers do the paper indicate for implementation of open science?
:::

>>>>

## Characteristics of the paper

-   Type of paper (e.g., tips, example): guide
-   Themes (e.g., tools, organization): organization
-   Other keywords (e.g., newcomers): team science, individual-centered

@@

@@

@@

@@

### 2024-10-22 doc/charting/Turoman-2022.qmd
making charting template and testing with a few studies
update data extraction from my studies

---
title: 'Charting form template'
---

::: content-hidden
fill in one form per paper. Name the form according to first author and
year like this: "Turoman-2022". Copy-paste the information from the
full-text review below.
:::

# title of publication

-   File:
-   DOI:
-   OpenAlex ID:

@@

::: content-hidden
For instance: "OSF - pre-registration - planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

-

@@

::: content-hidden
For instance: "Develop forms of legitimate peripheral participation."

These are bit of information and recommendations for governance of the
project.
:::

-

@@

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

-

## Educational perspectives

### Educational needs

::: content-hidden
For instance: "few resources for open collaboration, none were open and
they were valued poorly compared to other practices"

What does the paper write is the need for education in the field?
:::

@@

::: content-hidden
For instance: "lack of education"

Which barriers do the paper indicate for implementation of open science?
:::

-

>>>>

---
title: 'Turoman-2022'
---

# Open and reproducible practices in developmental psychology research: The workflow of the WomCogDev lab as an example

-   File: data/review/fulltext/oa-id-W4229452124.pdf
-   DOI: https://doi.org/10.31234/osf.io/73bwu
-   OpenAlex ID: https://openalex.org/W4229452124

## Characteristics of the paper

-   Type of paper (e.g., tips, example): example
-   Themes (e.g., tools, organization): tools, workflow
-   Other keywords (e.g., newcomers): lab-centered

@@

-   Slack - communication - all
-   Trello - project management - planning
-   Open Science Framework - repository - planning, analysing,
    dissemination
-   R - data analysis - analysing
-   Jasp - data analysis - analysing
-   Zenodo - data sharing - dissemination
-   OpenNeuro - data sharing - dissemination

@@

-   Setup a clear structure for how to conduct the research considering
    open science in each step
-   Build in steps for error correction

@@

-   designing the project - preregistration - creating the experiment -
    recruiting and data collection - data analysis - dissemination

@@

-   Not everyone have the same prerequisites. There are conscious
    tradeoffs between trying to be as open as possible, and the
    feasibility of applying an open practice
-   Some practices can take additional time
-   For the workflow to work, lab members must follow it quite closely
-   The learning curve can be steep, especially for people who arrive
    from more goal-oriented labs
